More than one Author with different Affiliations

### 2012-04-22 paper/ms.tex
Line breaks at 80

\date{Title and author order subject to change}

@@

\section{The Unknown Parameters}
There are $N$ stars in the field, where $N$ is unknown. Each star has an unknown position
$(x,y)$ in the plane of the sky, and an unknown flux $f$. We also
parameterise the {\it distribution} of positions by parameters $\alpha$,
and we parameterise the distribution of fluxes (aka the {\it luminosity function}) by parameters $\beta$.

In summary, the unknown parameters are:
\begin{eqnarray}
\theta = \left\{N, \alpha, \beta, \left\{x_i, y_i\right\}_{i=1}^N, \left\{f_i\right\}_{i=1}^N\right\}
\end{eqnarray}

@@

Here, we have assumed that the luminosity function 
(distribution of fluxes) does not depend on position.

>>>>

\date{{\bf Title and author order subject to change} \\
{\bf Also nag me if you prefer American English}}

@@

\section{The Unknown Parameters}
There are $N$ stars in the field, where $N$ is unknown. Each star has an unknown
position $(x,y)$ in the plane of the sky, and an unknown flux $f$. We also
parameterise the {\it distribution} of positions by parameters $\alpha$,
and we parameterise the distribution of fluxes (aka the {\it luminosity
function}) by parameters $\beta$. In summary, the unknown parameters are:
\begin{eqnarray}
\theta = \left\{N, \alpha, \beta, \left\{x_i, y_i\right\}_{i=1}^N, 
\left\{f_i\right\}_{i=1}^N\right\}
\end{eqnarray}

@@

Here, we have assumed that the luminosity function does not depend on position.
